The dependence of spiral disk morphology on the star formation-stellar mass relation

### 2014-07-30 mainsequence_morph.tex
Last edits from Zurich 2014 visit for KWW
Discussion & acknowledgedments
I updated the discussion at the bottom adding some key points on what I
think the result means. Also added my funding acknowledgements

@@

>>>>

%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Discussion text from KS}
Our results show that the star-forming main sequence is remarkably robust to the details of the spatial distribution of star formation \textit{within} galaxies. Testing for a wide range of morphological sub-types of star-forming disk galaxies yields no statistically significant difference in the relative position of these sub-types viz a vis the main sequence. The number or pitch angle of spiral arms and the presence or absence of a large-scale bar are not correlated with any detectable increase or decrease in the efficiency of star formation. The system which regulates star formation in galaxies is thus either not affected by the details of the spatial distribution of star formation, or its regulatory effect is so strong that it wipes out any such effect in a short time.

The most significant forcing event to the galaxy system known -- a major galaxy merger -- has only a slight effect. Star formation rates are increased by an average of X in major mergers. This shows just how stable the regulatory system in galaxies really is. Almost all simulations of galaxy mergers predict a steep increase in the star formation rate during first passage and final coalescence. The magnitude of this increase often depends on the details of the simulation, but can range from a factor of 10 to 100. In the low redshift universe sampled by SDSS and Galaxy Zoo, we find no evidence for an enhancement of such magnitude. This in turn suggests that the current generation of galaxy merger simulations miss a critical feedback mechanisms that prevents runaway peaks in star formation rates during mergers.
%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------

@@

KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1.
